Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
restate multideg

### Network metrics 
We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals within and across layers, and the similarity of
different layers. To measure the role of individuals within layers, we
calculated degree centrality and graph strength. Degree centrality is the number
of direct connections an individual has to other individuals in a network layer.
Graph strength is the degree weighted by the strength of association, in this
case SRI, in each layer. Extending degree centrality to multiple layers, we calculated multidegree,
the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
overlap. Edge overlap is defined as the proportion of edges present in each
network layer out of all observed edges  [@Battiston_2014]. Network metrics were
calculated using the R packages `igraph` [@Csardi_2006], `asnipe`
[@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table` [@Dowle_2019].

>>>>

### Network metrics 
We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals within and across layers, and the similarity of
different layers. To measure the role of individuals within layers, we
calculated degree centrality and graph strength. Degree centrality is the number
of direct connections an individual has to other individuals in a network layer.
Graph strength is the degree weighted by the strength of association, in this
case SRI, in each layer. We calculated multidegree,
the sum of degree centrality of individuals across layers, an extension
of degree centrality to multiple layers [@Berlingerio_2012;
@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
overlap. Edge overlap is defined as the proportion of edges present in each
network layer out of all observed edges  [@Battiston_2014]. Network metrics were
calculated using the R packages `igraph` [@Csardi_2006], `asnipe`
[@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table` [@Dowle_2019].
